Blocking-resistant communication\\through domain fronting

### 2014-08-01 docs/meek.tex
Anonymized LBL

% Avoid line breaks in program names.
\newcommand{\meekclient}{\mbox{meek-client}\xspace}
\newcommand{\meekserver}{\mbox{meek-server}\xspace}
\newcommand{\meek}{\texttt{meek}\xspace}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from Lawrence Berkeley National Laboratory (LBL),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The LBL trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{LBL Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the LBL traffic trace,
and \meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

We consider the duration of TCP connections as a potential distinguisher.
Figure~\ref{fig:duration} shows the cumulative probability
of connection durations in our two traces.
Considering the LBL trace first,
we see interesting probability concentrations on
round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
We hypothesize that this phenomenon is caused by
keepalive timeouts in web browsers and servers,
and polling behavior of web apps.
The small rise at 600 seconds is an artifact caused
by the fact that the trace is only 10 minutes long.
Connections lasting longer than 10 minutes are not accurately reflected,
however we can say that only about 8\% of connections lasted longer than 10 minutes.

The \meek trace shows a propensity for longer connections.
Over 4.5 hours, there were only 10 connections,
three of them lasting for an hour.
The long connections are caused by the client browser extension's
use of long-lived HTTP keepalive connections,
combined with \meekclient's polling requests,
which keep the connection from becoming idle.
The traffic trace represents the browsing of hundreds of web sites
and thousands of HTTPS transactions, but they all
occurred over just a few TCP/TLS connections.
60\% of \meek connections lasts five minutes or longer,
while only 13\% of those of ordinary traffic do.
\meek has essentially no connections lasting less than 24 seconds,
but such short connections account for over 42\% of the LBL HTTPS connections.
30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
evidently reflecting a built-in time limit in either the client browser extension
or in App Engine.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The LBL trace shows 2,745 unique clients and the \meek trace only one.
The dark line is a smoothed average number of connections per client.
The \meek count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the LBL trace is 2.61,
and in the \meek trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how \meek tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the LBL trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the LBL trace is 2.61,
while in the \meek trace it is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

% TODO: Since the average numbers of connections are quite different, reviewers may think
% it is remarkable. We should probably show a large percentage of users in the LBL trace only
% have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.

>>>>

% Avoid line breaks in program names.
\newcommand{\meekclient}{\mbox{meek-client}\xspace}
\newcommand{\meekserver}{\mbox{meek-server}\xspace}
\newcommand{\meek}{\texttt{meek}\xspace}
\newcommand{\lbl}{ResearchLab\xspace}
\def\urll#1{\begin{NoHyper}\url{#1}\end{NoHyper}}

@@

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~megabytes in all
and covers about 4.5 hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a research lab (anonymized as \lbl for blind submission),
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~megabytes of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we received the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the \lbl traffic trace,
and \meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

We consider the duration of TCP connections as a potential distinguisher.
Figure~\ref{fig:duration} shows the cumulative probability
of connection durations in our two traces.
Considering the \lbl trace first,
we see interesting probability concentrations on
round numbers: 10~s, 60~s, 120~s, 180~s, and 240~s.
We hypothesize that this phenomenon is caused by
keepalive timeouts in web browsers and servers,
and polling behavior of web apps.
The small rise at 600 seconds is an artifact caused
by the fact that the trace is only 10 minutes long.
Connections lasting longer than 10 minutes are not accurately reflected,
however we can say that only about 8\% of connections lasted longer than 10 minutes.

The \meek trace shows a propensity for longer connections.
Over 4.5 hours, there were only 10 connections,
three of them lasting for an hour.
The long connections are caused by the client browser extension's
use of long-lived HTTP keepalive connections,
combined with \meekclient's polling requests,
which keep the connection from becoming idle.
The traffic trace represents the browsing of hundreds of web sites
and thousands of HTTPS transactions, but they all
occurred over just a few TCP/TLS connections.
60\% of \meek connections lasts five minutes or longer,
while only 13\% of those of ordinary traffic do.
\meek has essentially no connections lasting less than 24 seconds,
but such short connections account for over 42\% of the \lbl HTTPS connections.
30\% (3 out of 10) of \meek's connections lasted almost exactly one hour,
evidently reflecting a built-in time limit in either the client browser extension
or in App Engine.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{concurrent.pdf}
\caption{
Number of simultaneous HTTPS connections to any Google server.
Each pale line indicates the number of HTTPS connections
of a single client IP address.
The \lbl trace shows 2,745 unique clients and the \meek trace only one.
The dark line is a smoothed average number of connections per client.
The \meek count stays close to~1 throughout, only momentarily
jumping to 0 or~2.
The average number of connections per user in the \lbl trace is 2.61,
and in the \meek trace is 1.002.
}
\label{fig:concurrent}
\end{figure}

The number of concurrent connections is another potential distinguisher.
We have seen how \meek tends to use one long-lived connection
through which it tunnels all its requests.
Figure~\ref{fig:concurrent} compares the number of concurrent HTTPS connections to
Google per client in both traces.
The number of connections in the \lbl trace is variable,
with some hosts briefly spiking up above 50 connections,
but the average case is very heavily skewed to smaller numbers.
The average number of connections in the \lbl trace is 2.61,
while in the \meek trace it is almost exactly 1, only briefly
deviating when one connection ends and another begins.
We conclude that having a small number of concurrent connections is unremarkable.

% TODO: Since the average numbers of connections are quite different, reviewers may think
% it is remarkable. We should probably show a large percentage of users in the \lbl trace only
% have 1~2 connections throughout. Therefore a \meek user is a needle in the haystack.
